Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-05 notes.tex
tried to calculate GF for dimer, ran into some problems, will check after dinner

>>>>

Armed with the expression for the momentum space Greens function, one can compute the real space local Green's function by summing over the momenta:
	G_H(\vec r = 0, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}
For the Hubbard dimer, the set of momenta are $0, \frac{\pi}{a}$, so
	\xi_{\vec k} = 2, -2
Therefore, the Greens function at $\vec r=0$ for the Hubbard dimer can be expressed as
	G_H(\vec r = 0, \omega) = \frac{1}{2}\left[\frac{1}{g_0 + 2g_1} + \frac{1}{g_0 - 2g_1}\right]  = \frac{g_0}{g_0^2 - 4g_1^2}
$g_{0,1}$ are expressed in terms of the elements of the inverse Greens function matrix of the Hubbard dimer. The inverse of a $2\times 2$ matrix is
	G_D^{-1} = \frac{1}{\text{Det }G_D}\begin{pmatrix} \left(G_D\right)_{00} &  -\left(G_D\right)_{01} \\ -\left(G_D\right)_{01} & \left(G_D\right)_{00}\end{pmatrix} \implies \begin{cases}
		g_0 = \frac{2}{2} \frac{1}{\text{Det }G_D}\left(G_D\right)_{00} \\
		\\
		g_1 = -\frac{2}{2\times 1}\frac{1}{\text{Det }G_D}\left(G_D\right)_{01} \\
	\end{cases}
Substituting these values into the expression gives
	G_H(\vec r = 0, \omega) = \text{Det }G_D\frac{g_0}{g_0^2 - 4g_1^2}
